Low Complexity Adaptive Beamformer\\ for Active Sonar Imaging

### 2015-08-09 LCAforActiveSonarImaging/lca.tex
la2pdf commit - 2015:08:09	15:53:36	(Sun 9.Aug)

\section{Steering a Kaiser window}

\begin{align}
w[n] = \begin{cases}
\frac{I_0\left(\pi\beta\sqrt{1-\left(\frac{2\pi}{N-1}-1\right)^2}\right)}{I_0(\pi\beta)}, & 0\le n\le N-1 \\
0 & \text{otherwise}
\end{cases}
\end{align}

α controls the tradeoff between main-lobe width and side-lobe area.  As α increases, the main lobe of W0(f) increases in width, and the side lobes decrease in amplitude, as illustrated in the figure at right.  α = 0 corresponds to a rectangular window. For large α, the shape of the Kaiser window (in both time and frequency domain) tends to a Gaussian curve.  The Kaiser window is nearly optimal in the sense of its peak's concentration around frequency 0 (Oppenheim et al., 1999).

>>>>

\section{Kaiser windows}

As will be demonstrated in upcoming sections, the LCA beamformer works very well with windows generated from the Kaiser-Bessel function. It is defined as:
%
\begin{align}
w_m = \begin{cases}
\frac{I_0\left(\pi\beta\sqrt{1-\left(\frac{m}{M/2}\right)^2}\right)}{I_0(\pi\beta)}, & 0\le |m|\le M/2 \\
0 & \text{otherwise}
\end{cases}
\end{align}
%
where $I_0$ is the zeroth order Modified Bessel function of the first kind, defined as:
%
\begin{align}
I_0(x) = \sumb{k=0}{\infty} \left[ \frac{\left(\frac{x}{2}\right)^k}{k!} \right].
\end{align}
%

As will be demonstrated in upcoming sections, the performance of the LCA beamformer is surprisingly similar regardless of what windows it is allowed to choose from. Therefore we have selected a 
% 
% 
% α controls the tradeoff between main-lobe width and side-lobe area.  As α increases, the main lobe of W0(f) increases in width, and the side lobes decrease in amplitude, as illustrated in the figure at right.  α = 0 corresponds to a rectangular window. For large α, the shape of the Kaiser window (in both time and frequency domain) tends to a Gaussian curve.  The Kaiser window is nearly optimal in the sense of its peak's concentration around frequency 0 (Oppenheim et al., 1999).
% 
% Narrow ones:
% - Best coherent gain, lowest equivalent noise bandwidth, and most sensitive to steering meaning not needing to steer as much for some effect.
% 
% 
% Beamforming:
% - Maximize resolution
% - Minimize noise/error, both coherent and incoherent
% - Minimize signal cancellation
% 
% Gauss: Miminized time-bandwidth product
%   - 
%   
% Rectangular
%   - 
% Dolph-Cheb: Minimize mainlobe width given sidelobe suppression
% Kaiser: For a restricted energy and time duration, maximize energy in the band of frequencies W.
% 
% Adaptive windows perform best in detection of closely separated angles of significantly amplitudes.
